Confidence Intervals for Prevalence Estimates from Complex Surveys with Imperfect Assays

### 2021-11-04 PrevAdjSurvey.tex
Updates from Overleaf

Let \( \hat{\theta}_i = \frac{X_i}{n_i} \), \( \hat{\phi}_n = \frac{C_n}{m_n} \), and \( \hat{\phi}_p = \frac{C_p}{m_p} \).
Then a natural estimator for \( \beta^* \) is

@@

First, we consider the scenario \( k = 1 \), \( \phi_n > 0 \), and \( \phi_p < 1 \).
We develop a confidence interval for the population prevalence, \( \beta^* \).
Because \( k = 1 \), the estimator in Equation~\ref{eq:long-beta} becomes

@@

We compare this method to one described in \cite{Lang:2014} as implemented in prevSeSp function in \cite{asht}, which provides approximate confidence intervals for true prevalence when sensitivity and specificity are estimated from independent samples, as they are in the in this section.

@@

\subsection{Estimating Prevalence from a Weighted Sample with a Perfect Assay}
\label{sec:weight-perfect}
Next, we develop a confidence interval for the population prevalence, \( \beta^* \), in the scenario \( k > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \).
Our method is a straightforward adaptation of the one presented in \cite{FayF:1997}, which was developed to create confidence intervals for a population rate which is assumed to a weighted sum of Poisson rate parameters.
We note that for sufficiently large sample size \( n \) and small rate \( \lambda \), a \( \operatorname{Poisson}(n\lambda) \) distribution is approximately equal in distribution to a \( \operatorname{Binomial}(n, \lambda) \) distribution.
Under this assumption, we suggest the confidence interval for \( \beta^* \):

@@

We also apply the methods to the subset of only hispanic participants (\( n = 1281, \text{weight coefficient of variation} = 306\% \)).
The Korn and Graubard type confidence distributions produce the 95\% confidence interval for population prevalence (2.35\%, 11.75\%), while the wsPoisson type confidence distributions produce the 95\% confidence interval (2.40\%, 20.02\%).

>>>>

Let \( \hat{\theta}_i = \frac{X_i}{n_i} \), \( \hat{\phi}_n = 1 - \frac{C_n}{m_n} \), and \( \hat{\phi}_p = \frac{C_p}{m_p} \).
Then a natural estimator for \( \beta^* \) is

@@

First, we consider the scenario0 \( k = 1 \), \( \phi_n > 0 \), and \( \phi_p < 1 \).
We develop a confidence interval for the population prevalence, \( \beta^* \).
Because \( k = 1 \), the estimator in Equation~\ref{eq:long-beta} becomes

@@

\todo[inline]{Can Mike provide some explanation for the form of this interval? Or some citation? Does it follow from Fay, Proschan, and Brittain (2015), or is there an intermediate reference?}

The quantiles of these melded distributions are calculated by Monte Carlo sampling from each of the component distributions.
We compare this method to one described in \cite{Lang:2014} as implemented in prevSeSp function in \cite{asht}, which provides approximate confidence intervals for true prevalence when sensitivity and specificity are estimated from independent samples, as they are in the in this section.

@@

\subsection{Estimating Prevalence from a Weighted Sample with a Perfect Assay}
\label{sec:weight-perfect}
Next, we develop a confidence interval for the population prevalence, \( \beta^* \), in the scenario \( k > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \).
Our method is a straightforward adaptation of the one presented in \cite{FayF:1997}, which was developed to create confidence intervals for a population rate which is assumed to a weighted sum of Poisson rate parameters.
We note that for sufficiently large sample size \( n \) and small rate \( \lambda \), a \( \operatorname{Poisson}(n\lambda) \) distribution is approximately equal in distribution to a \( \operatorname{Binomial}(n, \lambda) \) distribution.
Under this assumption, we suggest the \( a \)\% confidence interval for \( \beta^* \):

@@

We also apply the methods to the subset of only hispanic participants (\( n = 1281, \text{weight coefficient of variation} = 306\% \)).
The Korn and Graubard type confidence distributions produce the 95\% confidence interval for population prevalence (2.35\%, 11.75\%), while the wsPoisson type confidence distributions produce the 95\% confidence interval (2.40\%, 20.02\%).
\todo[inline] Maybe also compute with the non sensitivity/specificity adjusted interval.
